DATA 621---Business Analytics and Data Mining

### 2020-09-21 HW1/HW1_Group2.Rmd
Unused

## Performance
```{r performance}
##################### SELECT MODELS
# Model accuracy
results <- data.frame(
  Models = c("Model #1: Backwards" , "Model #2: Pairwise", "Model #3: K-fold"),
  R.squared = c(mod_sum1[["r.squared"]], stmr2, mod_sum3[["r.squared"]]), 
  adj.R.squared = c(mod_sum1[["adj.r.squared"]], stmar2,
                    mod_sum3[["adj.r.squared"]]),
  RSME = c(sqrt(mean(lm_1$residuals ^ 2)), stmRMSE,
           sqrt(mean(step.model$residuals ^ 2))),
  AIC = c(AIC(lm_1), AIC(stepModel), AIC(step.model)))
results %>% knitr::kable(digits = 3L, 
                         caption = 'Performance Statistics & Error Measure of Models')
```

```{r errors}

# calculate predictions for each model 
mod1_preds <- data.frame(cbind(train_df2$TARGET_WINS, round(mod_sum1$residuals,0), train_df2$TARGET_WINS + round(mod_sum1$residuals,0) ))
colnames(mod1_preds) <- c('TARGET_WINS', 'RESIDUAL', 'PREDICTED')

mod2_preds <- data.frame(cbind(ts2$TARGET_WINS, round(sstm$residuals,0), ts2$TARGET_WINS + round(sstm$residuals,0) ))
colnames(mod2_preds) <- c('TARGET_WINS', 'RESIDUAL', 'PREDICTED')

mod3_preds <- data.frame(cbind(stepdata.2$TARGET_WINS, round(mod_sum3$residuals,0), stepdata.2$TARGET_WINS + round(mod_sum3$residuals,0) ))
colnames(mod3_preds) <- c('TARGET_WINS', 'RESIDUAL', 'PREDICTED')

# summary statistics for residuals
resid_stats <- data.frame(rbind(summary(mod1_preds$RESIDUAL), summary(mod2_preds$RESIDUAL), summary(mod3_preds$RESIDUAL)))

resid_stats$Models <- c('Model #1: Backwards' , 'Model #2: Pairwise', 'Model #3: K-fold')

```

>>>>

## Performance
```{r performance}
# SELECT MODELS
# Model accuracy
results <- data.frame(
  Models = c("Model #1: Backwards" , "Model #2: Pairwise", "Model #3: K-fold"),
  R.squared = c(mod_sum1[["r.squared"]], stmr2, mod_sum3[["r.squared"]]), 
  adj.R.squared = c(mod_sum1[["adj.r.squared"]], stmar2,
                    mod_sum3[["adj.r.squared"]]),
  RSME = c(sqrt(mean(lm_1$residuals ^ 2)), stmRMSE,
           sqrt(mean(step.model$residuals ^ 2))),
  AIC = c(AIC(lm_1), AIC(stepModel), AIC(step.model)))
results %>% knitr::kable(digits = 3L, 
                         caption = 'Performance Statistics & Error Measure of Models')
```
